\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

% Ajuste das margens
\geometry{margin=1in}

% Comandos customizados
\newcommand{\heading}[1]{\noindent\textbf{\Large{#1}}}
\newcommand{\subheading}[1]{\noindent\textbf{\normalsize{#1}}} % Sem espaçamento extra

\begin{document}

\begin{center}
    {\huge \textbf{Luis Eduardo Alencar Duarte Franco}} \\
    Teresina, Piauí, Brasil \\
    \href{mailto:adf.luis@yahoo.com}{adf.luis@yahoo.com} \textbullet{} (86) 99986-2736 \\
    \href{https://github.com/seu-usuario}{GitHub} \textbullet{} \href{https://linkedin.com/in/seu-usuario}{LinkedIn}
\end{center}

\vspace{0.5cm}

\heading{Computer Science Student} \\ 
Eager to solve real problems, academic experience in agile, environment setup, Linux, CI/CD and more. Proactive, communicative and always ready to learn.

\vspace{0.5cm}

\heading{Education} \\
\textbf{Universidade Federal do Piauí} — Teresina, Piauí, Brasil \\
Bachelor's Degree in Computer Science (Jan 2019 - Dez 2026)

\vspace{0.5cm}

\heading{Projects}

\vspace{0.3cm}

\noindent
\subheading{\href{https://github.com/luisedu-adf/risc16}{RiSC-16 Processor Implementation}}  
\begin{itemize}[noitemsep]
    \item Developed using VHDL, GHDL and GTKWave, simulates the instruction-set of the RiSC-16 architecture. 
    \item Automated testing with bash scripts.
\end{itemize}


\noindent
\subheading{\href{https://github.com/es20231/eqp3}{Web App - CRUD for Imagens}}  
\begin{itemize}[noitemsep]
    \item RESTful API (Flask) integrated with React.js front-end.
	\item Agile Methodology applied with GitActions and colaborative work.
\end{itemize}


\noindent
\subheading{\href{https://github.com/luisedu-adf/chycho}{Web Scraper e Blog Redesign}}  
\begin{itemize}[noitemsep]
    \item Reconstruction of a blog using BeautifulSoup and MongoDB to scrape and store the data.
    \item Implemented in a EC2 AWS instance, keeping it online for a year.
\end{itemize}

\vspace{0.5cm}

\heading{Technical Skills}
\begin{itemize}[noitemsep]
    \item \textbf{Languages:} Python, Java, C, VHDL, HTML, CSS
    \item \textbf{Frameworks:} Flask, React.js
    \item \textbf{Testing:} CI/CD, Pytest, Selenium
    \item \textbf{Dabatases:} MySQL, SQLite, MongoDB
    \item \textbf{Tools:} Git, Postman, LaTeX, PlantUML
    \item \textbf{Idioms:} Fluent English
\end{itemize}

\vspace{0.5cm}


\heading{Certifications}
\begin{itemize}[noitemsep]
    \item \href{https://www.credly.com/badges/fe74fb6a-74be-44ed-be9a-71f450ec811a/linked_in_profile}{AWS Cloud Practitioner Certification}
\end{itemize}

\end{document}

